NGO analysis

### 2022-07-25 Shiny/Test/Dashboard downloads test.Rmd
So many changes.
Adding NGO title. Requiring purrr. Reformatting KPI details.

```{r setup, include=FALSE}
# Loading packages using pacman to ensure they're all installed
if (!require("pacman")) install.packages("pacman")
library(pacman)
p_load(
  shiny, tidyverse, scales, rvest, janitor, plotly, readxl,
  flexdashboard, MetBrewer, fontawesome, htmltools
)
# Using the fontawesome package for more up-to-date (and currently supported)
# Fontawesome icons
htmltools::tagList(fontawesome::fa_html_dependency())
```

@@

Enter the name of the NGO in the text box to include it in the report.

```{r sidebar_button}
textInput("name", "NGO name", value = "NGO name")
# download
uiOutput("downloadUI")
```

@@

@@

- **Fundraising ROI**: $$\frac{\text{private contributions} + \text{membership fees} - \text{fundraising expenses}}{\text{fundraising expenses}} \times 100$$
  - A basic measure of the ROI of direct fundraising expenses.
- **Liquid assets/obligations**: $$\frac{\text{private contributions} + \text{investment income} + \text{cash in bank and cash equivalents}}{\text{short term grants payable} + \text{revocable endowments} + \text{long term grants payable}} \times 100$$
  - A measure of the relationship between the organisation's liquid assets and its obligations.
- **Private donations growth**: $$\frac{\text{private contributions}_2 - \text{private contributions}_1}{\text{private contributions}_1}\times 100$$
  - A calculation of the percentage change in private contributions based on the two most recent years.
- **Public grants growth**: $$\frac{\text{public grants}_2 - \text{public grants}_1}{\text{public grants}_1} \times 100$$
  - A calculation of the percentage change in public grants received based on the two most recent years.
- **Private/public proportion**: $$\frac{\text{private contributions} + \text{membership fees}}{\text{public grants} + \text{private contributions} + \text{membership fees}} \times 100$$
  - Calculates the percentage of non-commercial or activity-based income that is derived from private contributions and membership fees as opposed to public grants.

@@

    params <- list(
      htmlfile = input$html$datapath,
      excelfile = input$excel$datapath,
      start = input$start,
      end = input$end,
      title = input$name
    )

@@

>>>>

```{r setup, include=FALSE}
# Loading packages using pacman to ensure they're all installed
if (!require("pacman")) install.packages("pacman")
library(pacman)
p_load(
  shiny, tidyverse, scales, rvest, janitor, plotly, readxl,
  flexdashboard, MetBrewer, fontawesome, htmltools, purrr
)
# Using the fontawesome package for more up-to-date (and currently supported)
# Fontawesome icons
htmltools::tagList(fontawesome::fa_html_dependency())
```

@@

```{r sidebar_button}
# download
uiOutput("downloadUI")
```

@@

Row {data-height=60}
-----------------------------------------------------------------------

### NGO analysed

```{r}
# Using htmlOutput() to use html styling
htmlOutput("title")
```

@@

- **Fundraising ROI**:
  - A basic measure of the return on investment of direct fundraising expenses:

  $$\frac{\text{private contributions} + \text{membership fees} - \text{fundraising expenses}}{\text{fundraising expenses}} \times 100$$

- **Liquid assets/obligations**:
  - A measure of the relationship between the organisation's liquid assets and its obligations:

  $$\frac{\text{private contributions} + \text{investment income} + \text{cash in bank and cash equivalents}}{\text{short term grants payable} + \text{revocable endowments} + \text{long term grants payable}} \times 100$$

- **Private donations growth**:
  - A calculation of the percentage change in private contributions based on the two most recent years:

  $$\frac{\text{private contributions}_2 - \text{private contributions}_1}{\text{private contributions}_1}\times 100$$

- **Public grants growth**:
  - A calculation of the percentage change in public grants received based on the two most recent years:

$$\frac{\text{public grants}_2 - \text{public grants}_1}{\text{public grants}_1} \times 100$$

- **Private/public proportion**:
  - Calculates the percentage of non-commercial or activity-based income that is derived from private contributions and membership fees as opposed to public grants:

$$\frac{\text{private contributions} + \text{membership fees}}{\text{public grants} + \text{private contributions} + \text{membership fees}} \times 100$$

@@

    params <- list(
      htmlfile = input$html$datapath,
      excelfile = input$excel$datapath,
      start = input$start,
      end = input$end
    )

@@

  # NGO title ==================================================================
  NGO <- reactive({
    read_excel(input$excel$datapath) |>
      # Turning the needed column into a list
      pull(Firm) |>
      # discarding all NAs in case the name is somewhere
      purrr::discard(is.na) |>
      # choosing the first available name
      first()
  })

  title <- reactive({
    # testing if NGO() is NA
    if (is.na(NGO())) {
      # Printing warning if NA
      "Name of NGO missing"
      # Printing name of NGO
    } else {
      NGO()
    }
  })

  # Creating NGO title using html formatting (colour based on MetBrewer
  # "Hokusai2")
  output$title <- renderText({
    paste('<b><font size="5em" color="#2f70a1">', title(), "</font></b>")
  })
